Modern Graph Generators: A Survey

### 2018-11-10 challenges.tex
Minor corrections befor re-submitting

The respective data generator should hence be able to simulate a natural growth
and/or changes in the structure of the graph with regards to the various
features of distinct use cases. However,  even though the area of dynamic graphs
is intensively studied, surprisingly there seem to exist only very few proposals
of a generator for dealing with this area.
In~\cite{GoerkeKlugeSchumm2012_1000029825} the authors focus on \emph{clustering
dynamic graphs}, i.e. graphs where the clustering corresponds to the partition
of nodes into natural groups based on the paradigm of intra-cluster density
versus inter-cluster sparsity of edges. The generator generates a time series
of random graphs $G_0, G_1, ..., G_n$, where $G_t$ emerges from $G_{t-1}$ via
successive atomic updates like for instance, the insertion of a vertex or the removal of an
edge. The generator monitors the (dynamic) ground truth clustering and the probability
of the atomic events is chosen in such a way that the ground truth clustering is
maintained while the randomness of the generated grpah is kept.

>>>>

The respective data generator should hence be able to simulate a natural growth
and/or changes in the structure of the graph with regards to the various
features of distinct use cases. However,  even though the area of dynamic graphs
is intensively studied, surprisingly there seem to exist only very few proposals
of a generator for dealing with this area.
In~\cite{GoerkeKlugeSchumm2012_1000029825} the authors focus on \emph{clustering
dynamic graphs}, i.e. graphs where the clustering corresponds to the partition
of nodes into natural groups based on the paradigm of intra-cluster density
versus inter-cluster sparsity of edges. The generator generates a time series
of random graphs $G_0, G_1, ..., G_n$, where $G_t$ emerges from $G_{t-1}$ via
successive atomic updates like for instance, the insertion of a vertex or the removal of an
edge. The generator monitors the (dynamic) ground truth clustering and the probability
of the atomic events is chosen in such a way that the ground truth clustering is
maintained while the randomness of the generated graph is kept.

### 2018-11-10 data_sets.tex
Minor corrections befor re-submitting

Large scale graph analytics systems are usually benchmarked using a combination of
real-world and synthetically generated graphs. Because of the rapid evolution of such
systems and their increasing capability to process larger graphs, the datasets
typically used  in the literature quickly change overtime. The most commonly
used datasets (which can be downloaded from several graph dataset
repositories~\cite{snapnets,lawalgo}) are:
\begin{itemize}
  \item \textbf{DBLP}~\cite{yang2015defining}: Represents a co-authorship network where
    researchers from DBLP are represented as vertices and there exists an edge
    between them if they have published a paper together.
  \item \textbf{Amazon}~\cite{yang2015defining}: Represents a product co-purchasing
    network, such that each vertex represents a product while edges between two products
    exists if a person bought both of them.
  \item \textbf{Road networks}~\cite{leskovec2009community}: Consist of a set of road
    networks from the US.
  \item \textbf{LiveJournal}~\cite{yang2015defining}: A social network where vertices
    represent the users and the edges the acquitances between them.
  \item \textbf{Orkut}~\cite{yang2015defining}: Like LiveJournal, this is a social network
    where vertices represent persons and the edges their friendships.
  \item \textbf{Twitter}~\cite{kwak2010twitter}: This is a directed network representing
    the follower-followee interaction of Twitter.
  \item \textbf{Friendster}~\cite{yang2015defining}: A social network like LiveJournal and
    Orkut, where nodes represent persons and edges their relationships.
  \item \textbf{WebUK}~\cite{delis}: A web graph of the UK subdomain, where nodes represent
    websites and edges represent the hyperlinks between them.
  \item \textbf{ClueWeb2012}~\cite{clueweb}. This is a crawl of the web from 2012, where
    vertices represent websites and the edges represent the hyperlinks connecting them.
\end{itemize}

@@

Another application using social network data is that of assessing the degree of
reputation of a user based on their past interactions and
rankings~\cite{kamvar2003eigentrust,katz2006social,kumar2016edge}. Such
algorithms are typically evaluated on networks with explicit user rankings or
votings from other users, being the most widely used datasets the following
examples:

  \begin{itemize}
    \item \textbf{Bitcoin}~\cite{moore2013beware}: This dataset contains information from
      several Bitcoin exchanges, where users are able to rate other users after
      their transactions. Here, the vertices represent the users and the edges,
      which are labelled, the ratings between them.
    \item \textbf{Wikipedia RFA}~\cite{west2014exploiting}: This network is extracted
      from Wikipedia and the vertices represent users  while the
      edges, which are labelled, the votes emitted by administrators for the
      user to become an administrator.  Each vote is accompained with a text
      explaining the vote's sign.
    \item \textbf{WikiSigned}~\cite{maniu2011building}: This is a network of Wikipedia
      editors where the vertices are the editors and the edges, which are
      labelled, represent the trust level between two editors.
    \item \textbf{Extended Epinions}~\cite{massa2007trust}: This is an extended version of
      the Epinions network which also contains the levels of distrust between the
      users, expressed by means of edges between them.
    \item \textbf{Twitter Indian Elections}~\cite{kagan2015using}: This network represents
      a Twitter network where vertices represent users and there is an edge
      between two users if a user mentions another one in a tweet. The edges
      are labelled with the average sentiment of one user towards another.
  \end{itemize}

@@

\begin{itemize}
  \item \textbf{DBLP}, \textbf{Amazon}, \textbf{LiveJournal}, \textbf{Orkut} and \textbf{Friendster}~\cite{yang2015defining}
    are widely used for evaluating community detection since they provide
    information about the meta-communities they contain. For instance, in
    Livejournal, users can join groups of users talking about given topics. Such
    groups are exported as meta-communities, and similar approaches are used for
    other graphs. Community detection algorithms are then evaluated by trying to
    infer such meta-communities without prior knowledge of the user to group
    assignment.
  \item \textbf{Zachary Karate Club}~\cite{zachary1977information}: This graph consists
    of a small network of members of a karate club that was dismissed and split
    into two new karate clubs. Vertices represent persons and edges friendship
    relationships. Information about what people joined each of the two new
    karate clubs is provided.
  \item \textbf{PolBlogs}~\cite{adamic2005political}: This is a network consisting of
    blogs talking about the US 2005 political elections, where a vertex
    represents a blog and the edges the hyperlinks between the blogs. Each blog
    has an associated label, whether it is left or right oriented.
  \item \textbf{PolBooks}~\cite{10dimacs}: Is a network of books of Amazon that talk
    about politics, and edges between two books exist if they are co-purchased
    together. The books have labels of whether they are left or right oriented.
  \item \textbf{Football}~\cite{girvan2002network}: This network represent American university
    football teams. Each node is a football team and the edges are those 
    games between teams during the season. Each team is associated to a
    division.
\end{itemize}

>>>>

Large scale graph analytics systems are usually benchmarked using a combination of
real-world and synthetically generated graphs. Because of the rapid evolution of such
systems and their increasing capability to process larger graphs, the datasets
typically used  in the literature quickly change overtime. The most commonly
used datasets (which can be downloaded from several graph dataset
repositories~\cite{snapnets,lawalgo}) are:
\begin{itemize}
  \item \textbf{DBLP}~\cite{yang2015defining}: Represents a co-authorship network where
    researchers from DBLP are represented as vertices and there exists an edge
    between them if they have published a paper together.
  \item \textbf{Amazon}~\cite{yang2015defining}: Represents a product co-purchasing
    network, such that each vertex represents a product, while edges between two products
    exists if a person bought both of them.
  \item \textbf{Road networks}~\cite{leskovec2009community}: Consist of a set of road
    networks from the US.
  \item \textbf{LiveJournal}~\cite{yang2015defining}: A social network where vertices
    represent the users and the edges the acquittances between them.
  \item \textbf{Orkut}~\cite{yang2015defining}: Like LiveJournal, this is a social network
    where vertices represent persons and the edges their friendships.
  \item \textbf{Twitter}~\cite{kwak2010twitter}: This is a directed network representing
    the follower-followee interaction of Twitter.
  \item \textbf{Friendster}~\cite{yang2015defining}: A social network like LiveJournal and
    Orkut, where nodes represent persons and edges their relationships.
  \item \textbf{WebUK}~\cite{delis}: A web graph of the UK subdomain, where nodes represent
    websites and edges represent the hyperlinks between them.
  \item \textbf{ClueWeb2012}~\cite{clueweb}. This is a crawl of the web from 2012, where
    vertices represent websites and the edges represent the hyperlinks connecting them.
\end{itemize}

@@

Another application using social network data is that of assessing the degree of
reputation of a user based on their past interactions and
rankings~\cite{kamvar2003eigentrust,katz2006social,kumar2016edge}. Such
algorithms are typically evaluated on networks with explicit user rankings or
voting from other users, being the most widely used datasets the following
examples:

  \begin{itemize}
    \item \textbf{Bitcoin}~\cite{moore2013beware}: This dataset contains information from
      several Bitcoin exchanges, where users are able to rate other users after
      their transactions. Here, the vertices represent the users and the edges,
      which are labelled, the ratings between them.
    \item \textbf{Wikipedia RFA}~\cite{west2014exploiting}: This network is extracted
      from Wikipedia and the vertices represent users, while the
      edges, which are labelled, the votes emitted by administrators for the
      user to become an administrator.  Each vote is accompanied with a text
      explaining the vote's sign.
    \item \textbf{WikiSigned}~\cite{maniu2011building}: This is a network of Wikipedia
      editors where the vertices are the editors and the edges, which are
      labelled, represent the trust level between two editors.
    \item \textbf{Extended Epinions}~\cite{massa2007trust}: This is an extended version of
      the Epinions network which also contains the levels of distrust between the
      users, expressed by means of edges between them.
    \item \textbf{Twitter Indian Elections}~\cite{kagan2015using}: This network represents
      a Twitter network where vertices represent users and there is an edge
      between two users if a user mentions another one in a tweet. The edges
      are labelled with the average sentiment of one user towards another.
  \end{itemize}

@@

\begin{itemize}
  \item \textbf{DBLP}, \textbf{Amazon}, \textbf{LiveJournal}, \textbf{Orkut} and \textbf{Friendster}~\cite{yang2015defining}
    are widely used for evaluating community detection since they provide
    information about the meta-communities they contain. For instance, in
    Livejournal, users can join groups of users talking about given topics. Such
    groups are exported as meta-communities, and similar approaches are used for
    other graphs. Community detection algorithms are then evaluated by trying to
    infer such meta-communities without prior knowledge of the user to group
    assignment.
  \item \textbf{Zachary Karate Club}~\cite{zachary1977information}: This graph consists
    of a small network of members of a karate club that was dismissed and split
    into two new karate clubs. Vertices represent persons and edges friendship
    relationships. Information about what people joined each of the two new
    karate clubs is provided.
  \item \textbf{PolBlogs}~\cite{adamic2005political}: This is a network consisting of
    blogs talking about the US 2005 political elections, where a vertex
    represents a blog and the edges the hyperlinks between the blogs. Each blog
    has an associated label, whether it is left or right oriented.
  \item \textbf{PolBooks}~\cite{10dimacs}: Is a network of books of Amazon that talk
    about politics, and edges between two books exist if they are co-purchased
    together. The books have labels of whether they are left or right oriented.
  \item \textbf{Football}~\cite{girvan2002network}: This network represents American university
    football teams. Each node is a football team and the edges are games between teams during the season. Each team is associated to a
    division.
\end{itemize}

### 2018-11-10 generators_LinkedData.tex
Minor corrections befor re-submitting

\paragraph{Data Coherence}  A comparison of 4 RDF benchmarks (namely TPC-H~\cite{TPC-H} data expressed in RDF, LUBM, BSBM, and SP$^2$Bench) and 6 real-wold data sets (such as, e.g.,  DBpedia, the Barton Libraries Dataset~\cite{barton-benchmark} or
WordNet~\cite{Miller:1995:WLD:219717.219748}) has been reported by~\cite{Duan:2011:AOC:1989323.1989340}. The authors focus mainly on the  \emph{structuredness} (\emph{coherence}) of each benchmark dataset claiming that a primitive metric (e.g., the number of triples or the average in/outdegree) quantifies only some specific aspect of each dataset. The degree of structuredness of a dataset $D$ with respect to a type $T$ is based on  the regularity of instance data in $D$ on conforming to type $T$. The type system is extracted from the data set by finding the RDF triples that have property  \texttt{http://www.w3.org/1999/02/22-rdf-syntax-ns\#type} and extract type $T$ from their object. Properties of $T$ are determined as the union of all the properties that the instances of type $T$ have. The structuredness is then expressed as a weighted sum of share of set properties of each type, whereas higher weights are assigned to types with more instances. The authors show that the structuredness of the chosen benchmarks is fixed, whereas real-world RDF datasets lie in currently untested parts of the spectrum. As a consequence, they introduce a new benchmark that accepts as input any dataset associated with a required level of structuredness and size (smaller than the size of the original data), and exploits the input documents as a seed to generate a subset of the original data with the target structuredness and size. In addition, they show that structuredness and size mutually influence each other.

\paragraph{DBPSB} DBpedia SPARQL Benchmark (DBPSB)\footnote{\url{http://aksw.org/Projects/DBPSB.html}} proposed at the University of Leipzig is based on queries that have been issued by humans and applications
against existing RDF data~\cite{Morsey2011,Morsey:2012:UBR:2900929.2901031}. In addition, the authors argue that benchmarks like LUBM, BSBM, or SP$^2$Bench resemble relational database benchmarks involving relational data structures with few and homogeneously structured classes, whereas RDF knowledge bases are increasingly heterogeneous. For example, DBpedia version 3.6 consists of 289,016 classes of which 275 classes are defined based on the DBpedia ontology. In addition, different datatypes and object references of various types are
used in property values. Hence, they presented a generic SPARQL benchmark creation approach which is based on a flexible data generation mechanism that mimics the input data source. The proposed dataset creation process starts with an input dataset. Multiple Datasets with different sizes  are then generated by duplicating all triples and changing their namespaces.  For generating smaller datasets, an appropriate fraction of all triples is selected randomly or by sampling across classes in the dataset. \iffalse The goal of the query analysis and clustering is to detect prototypical queries on the basis of their frequent usage and similarity.\fi The methodology is applied on the DBpedia SPARQL endpoint and a set of 25 SPARQL query templates is derived, that cover the most commonly used SPARQL features.

@@

\paragraph{Geographica} The Geographica benchmark\footnote{\url{http://geographica.di.uoa.gr/}} has been designed to target the area of geospatial data~\cite{DBLP:conf/semweb/GarbisKK13} and respective SPARQL extensions GeoSPARQL~\cite{battle2012enabling} and stSPARQL~\cite{koubarakis2010modeling}. The benchmark involves a real-world workload based on openly available datasets that cove a range of geometry types (e.g., points, lines, polygons) and  a synthetic workload. In the former case there is a (1) a micro benchmark that tests primitive spatial functions (involving 29 queries) and (2) macro benchmark that tests the performance of RDF stores in typical application scenarios like reverse geocoding or map search and browsing (consisting of 11 queries). In the latter case of a synthetic workload the generator produces synthetic datasets of various sizes that corresponds to an ontology based on OpenStreetMap (i.e., states in a country, land ownership, roads and  points of interest) and instantiates query templates. The spatial extent of the land ownership dataset constitutes a uniform grid of $n \times n$ hexagons, whereas the size of each dataset is given relatively to $n$. The synthetic workload generator produces SPARQL queries corresponding to spatial selection and spatial joins by instantiating 2 query templates.

@@

\paragraph{RBench} RBench~\cite{Qiao:2015:RAR:2723372.2746479} is an application-specific benchmark which receives any RDF dataset as an input and produces as an output a set of datasets, that have similar characteristics of the input dataset, using size scaling factor $s$ and (node) degree scaling factor $d$. \iffalse A generated benchmark dataset is considered similar to the given dataset if their values for the dataset evaluation metrics and query evaluation times for different techniques are similar. Three evaluation metrics are utilized for this purpose: dataset coherence (i.e., a measure how uniformly predicates are distributed among the same type/class), relationship specialty (i.e., the number of occurrences of the same predicate associated with each resource), and literal diversity.\fi A query generation process has been implemented to produce 5 different types of queries (edge-based queries, node-based queries, path queries, star queries, subgraph queries) for any generated data. The benchmark project FEASIBLE~\cite{Saleem2015} is also an application-specific benchmark; however, contrary to RBench, it is designed to produce benchmarks from a set of queries (in particular from query logs) by relying on example queries of a user-defined
size from the input set of queries.

>>>>

\paragraph{Data Coherence}  A comparison of 4 RDF benchmarks (namely TPC-H~\cite{TPC-H} data expressed in RDF, LUBM, BSBM, and SP$^2$Bench) and 6 real-wold data sets (such as, e.g.,  DBpedia, the Barton Libraries Dataset~\cite{barton-benchmark} or
WordNet~\cite{Miller:1995:WLD:219717.219748}) has been reported by~\cite{Duan:2011:AOC:1989323.1989340}. The authors focus mainly on the  \emph{structuredness} (\emph{coherence}) of each benchmark dataset claiming that a primitive metric (e.g., the number of triples or the average in/outdegree) quantifies only some specific aspect of each dataset. The degree of structuredness of a dataset $D$ with respect to a type $T$ is based on  the regularity of instance data in $D$ in conforming to type $T$. The type system is extracted from the data set by finding the RDF triples that have property  \texttt{http://www.w3.org/1999/02/22-rdf-syntax-ns\#type} and extract type $T$ from their object. Properties of $T$ are determined as the union of all the properties that the instances of type $T$ have. The structuredness is then expressed as a weighted sum of share of set properties of each type, whereas higher weights are assigned to types with more instances. The authors show that the structuredness of the chosen benchmarks is fixed, whereas real-world RDF datasets lie in currently untested parts of the spectrum. As a consequence, they introduce a new benchmark that accepts as input any dataset associated with a required level of structuredness and size (smaller than the size of the original data), and exploits the input documents as a seed to generate a subset of the original data with the target structuredness and size. In addition, they show that structuredness and size mutually influence each other.

\paragraph{DBPSB} DBpedia SPARQL Benchmark (DBPSB)\footnote{\url{http://aksw.org/Projects/DBPSB.html}} proposed at the University of Leipzig is based on queries that have been issued by humans and applications
against existing RDF data~\cite{Morsey2011,Morsey:2012:UBR:2900929.2901031}. In addition, the authors argue that benchmarks like LUBM, BSBM, or SP$^2$Bench resemble relational database benchmarks involving relational data structures with few and homogeneously structured classes, whereas RDF knowledge bases are increasingly heterogeneous. For example, DBpedia version 3.6 consists of 289,016 classes of which 275 classes are defined based on the DBpedia ontology. In addition, different datatypes and object references of various types are
used in property values. Hence, they presented a generic SPARQL benchmark creation approach which is based on a flexible data generation mechanism that mimics the input data source. The proposed dataset creation process starts with an input dataset. Multiple datasets with different sizes  are then generated by duplicating all triples and changing their namespaces.  For generating smaller datasets, an appropriate fraction of all triples is selected randomly or by sampling across classes in the dataset. \iffalse The goal of the query analysis and clustering is to detect prototypical queries on the basis of their frequent usage and similarity.\fi The methodology is applied on the DBpedia SPARQL endpoint and a set of 25 SPARQL query templates is derived, that cover the most commonly used SPARQL features.

@@

\paragraph{Geographica} The Geographica benchmark\footnote{\url{http://geographica.di.uoa.gr/}} has been designed to target the area of geospatial data~\cite{DBLP:conf/semweb/GarbisKK13} and respective SPARQL extensions GeoSPARQL~\cite{battle2012enabling} and stSPARQL~\cite{koubarakis2010modeling}. The benchmark involves a real-world workload based on openly available datasets that cover a range of geometry types (e.g., points, lines, polygons) and  a synthetic workload. In the former case there is a (1) a micro benchmark that tests primitive spatial functions (involving 29 queries) and (2) macro benchmark that tests the performance of RDF stores in typical application scenarios like reverse geocoding or map search and browsing (consisting of 11 queries). In the latter case of a synthetic workload the generator produces synthetic datasets of various sizes that corresponds to an ontology based on OpenStreetMap (i.e., states in a country, land ownership, roads and  points of interest) and instantiates query templates. The spatial extent of the land ownership dataset constitutes a uniform grid of $n \times n$ hexagons, whereas the size of each dataset is given relatively to $n$. The synthetic workload generator produces SPARQL queries corresponding to spatial selection and spatial joins by instantiating 2 query templates.

@@

\paragraph{RBench} RBench~\cite{Qiao:2015:RAR:2723372.2746479} is an application-specific benchmark which receives any RDF dataset as an input and produces as an output a set of datasets, that have similar characteristics of the input dataset, using size scaling factor $s$ and (node) degree scaling factor $d$. \iffalse A generated benchmark dataset is considered similar to the given dataset if their values for the dataset evaluation metrics and query evaluation times for different techniques are similar. Three evaluation metrics are utilized for this purpose: dataset coherence (i.e., a measure how uniformly predicates are distributed among the same type/class), relationship specialty (i.e., the number of occurrences of the same predicate associated with each resource), and literal diversity.\fi A query generation process has been implemented to produce 5 different types of queries (edge-based queries, node-based queries, path queries, star queries, subgraph queries) for any generated data. The benchmark project FEASIBLE~\cite{Saleem2015} is also an application-specific benchmark; however, contrary to RBench, it is designed to produce benchmarks from a set of queries (in particular from query logs) by relying on sample queries of a user-defined
size from the input set of queries.

### 2018-11-10 generators_SocialNetworks.tex
Minor corrections befor re-submitting

\paragraph{Linkage vs. Activity Graphs} \cite{Yao2011} distinguished between two
types of social network graphs -- the \emph{linkage graph}, where nodes represent people and edges correspond to their friendships, and the \emph{activity graph}, where nodes also represent people but correspond to their interactions. On the basis of the analysis of
Flickr\footnote{\url{https://www.flickr.com/}} social links and
Epinions\footnote{\url{http://www.epinions.com/}} network of user interactions, the authors discover that they both exhibit high clustering coefficient (community structure), small diameter, and power-law degree distribution. Considering the dynamic properties they both have relatively stable clustering coefficient over time and follow the densification law. On the other hand, diameter shrinking is not observed in Epinions activity graph and there is a difference in degree
correlation (i.e., frequency of mutual connections of similar nodes) -- linkage graphs have positive, activity graphs neutral degree correlation. With regards to the findings, the proposed generator focusses on linkage graphs with positive degree correlation. For this purpose it extends the forest fire spreading process algorithm~\cite{Leskovec:2005:GOT:1081870.1081893} with
link symmetry. It has two parameters the \emph{burning probability} $P_b$ and \emph{symmetry probability} $P_s$. $P_b$ ensures a BFS-based forward burning process in which fire burns strongly with $P_b$ approaching 1.  $P_s$ ensures backward linking from old nodes to new nodes and ``adds fuel to the fire as it brings more links''. %It gives chances for big nodes to connect back to big nodes.

@@

\paragraph{LDBC SNB} Despite having a common Facebook-like dataset, thanks to three distinct workloads the Social Network Benchmark (SNB)~\cite{Erling:2015:LSN:2723372.2742786} provided by LDBC corresponds to three distinct benchmarks. The network nodes correspond to people and the edges represent their friendship and messages they post in discussion trees on their forums. The three query workloads involve: (1) SNB-Interactive, i.e., complex read-only queries accessing a significant portion of data, (2) SNB-BI, i.e., queries accessing a high percentage of  entities and grouping them in various dimensions, and (3) SNB-Algorithms, involving graph analysis algorithms, such as community detection, PageRank, BFS, and clustering. The graph generator realizes power laws, uses skewed value distributions, and ensures reasonable correlations between graph structures and property values. To provide scalability it is implemented on top of Hadoop.

>>>>

\paragraph{Linkage vs. Activity Graphs} \cite{Yao2011} distinguished between two
types of social network graphs -- the \emph{linkage graph}, where nodes represent people and edges correspond to their friendships, and the \emph{activity graph}, where nodes also represent people but correspond to their interactions. On the basis of the analysis of
Flickr\footnote{\url{https://www.flickr.com/}} social links and
Epinions\footnote{\url{http://www.epinions.com/}} network of user interactions, the authors discover that they both exhibit high clustering coefficient (community structure), small diameter, and power-law degree distribution. Considering the dynamic properties they both have relatively stable clustering coefficient over time and follow the densification law. On the other hand, diameter shrinking is not observed in Epinions activity graph and there is a difference in degree
correlation (i.e., frequency of mutual connections of similar nodes) -- linkage graphs have positive degree correlation, activity graphs have neutral degree correlation. With regards to the findings, the proposed generator focusses on linkage graphs with positive degree correlation. For this purpose it extends the forest fire spreading process algorithm~\cite{Leskovec:2005:GOT:1081870.1081893} with link symmetry. It has two parameters: the \emph{burning probability} $P_b$ and the \emph{symmetry probability} $P_s$. $P_b$ ensures a BFS-based forward burning process in which fire burns strongly with $P_b$ approaching 1.  $P_s$ ensures backward linking from old nodes to new nodes and ``adds fuel to the fire as it brings more links''. %It gives chances for big nodes to connect back to big nodes.

@@

\paragraph{LDBC SNB} Despite having a common Facebook-like dataset, thanks to three distinct workloads the Social Network Benchmark (SNB)~\cite{Erling:2015:LSN:2723372.2742786} provided by LDBC represents three distinct benchmarks. The network nodes correspond to people and the edges represent their friendship and messages they post in discussion trees on their forums. The three query workloads involve: (1) SNB-Interactive, i.e., complex read-only queries accessing a significant portion of data, (2) SNB-BI, i.e., queries accessing a high percentage of  entities and grouping them in various dimensions, and (3) SNB-Algorithms, involving graph analysis algorithms, such as community detection, PageRank, BFS, and clustering. The graph generator realizes power laws, uses skewed value distributions, and ensures reasonable correlations between graph structures and property values. To provide scalability it is implemented on top of Hadoop.
